---
title: "Main analysis"
author: "Kate Tran"
date: "7/7/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Library
```{r}
library(sjPlot) 
library(stringr)
library(performance)
library(janitor)
library(dplyr)
library(purrr)
library(qgraph)
library(caret)
library(corrplot)
library(cv)
library(iml)
library(randomForest)
library(ggplot2)
library(naniar)
source("../utility_fun.R")
source("../config.R")
```

# Read data
```{r}
data_long <- read.csv("../data/dataset_long.csv")
```

# Create discovery and testing subsets
```{r}
# ABCD dataset 1 & 2
abcd_gr1 <- readRDS("../outputs/abcd_gr1.rds")
abcd_gr2 <- readRDS("../outputs/abcd_gr2.rds")
vars <- readRDS("../outputs/vars_98.rds")
```

# Run univariate models
```{r}
# Exwas 1 on original variables - get significant variables - Not FDR corrected p-values for headache project - No covariates
exwas_headache <- exwas(data_train = abcd_gr1, vars = vars, outcome = "medhx_2q_l", data_test = abcd_gr2)
univariate_headache <- exwas_headache$univariate_models_dat

# eTable3
univariate_headache_sig <- exwas_headache$univariate_models_sig %>% 
    mutate(low_ci = round(exp(low_ci), 2), high_ci = round(exp(high_ci), 2), 
           CI_90 = paste0(low_ci, " - ", high_ci), p_value = round(p_value, 3)) %>% 
    select(variable, OR, CI_90, p_value) %>% 
    arrange(OR)

write.csv(univariate_headache_sig, "../outputs/univariate_headache_sig_070523.csv")

sig_vars <- univariate_headache_sig %>% pull(variable)

saveRDS(univariate_headache, file = "../outputs/univariate_plot_abcdgr1_coef_070523.rds")
```

# Check correlation of significant variables
```{r}
cor_vars <- abcd_gr1 %>% select(all_of(sig_vars))
corrs = cor_auto(cor_vars)
```

# Check missing frequency of significant variables
```{r}
data_long %>% filter(eventname == "baseline_year_1_arm_1") %>% select(all_of(sig_vars)) %>% miss_var_summary() %>% mutate(eventname = "Baseline") %>%
    bind_rows(data_long %>% filter(eventname == "1_year_follow_up_y_arm_1") %>% select(all_of(sig_vars)) %>% miss_var_summary() %>% mutate(eventname = "1-Year follow-up")) %>%
    bind_rows(data_long %>% filter(eventname == "2_year_follow_up_y_arm_1") %>% select(all_of(sig_vars)) %>% miss_var_summary() %>% mutate(eventname = "2-Year follow-up")) %>%
    tidyr::pivot_wider(., names_from = eventname, values_from = c(n_miss, pct_miss)) %>% View()
```

# Generate exposome score
```{r}
# Get weight from abcd_gr1 # but use binary variables of Likert variables only
# Exwas 2 on updated variables (with binary variables) - get coefficients
sig_vars_bin <- sig_vars
# Dichotomize 2 Likert variables
sig_vars_bin[sig_vars_bin == "tbi_ss_worst_overall_l"] <- "tbi_worst_overall"
sig_vars_bin[sig_vars_bin == "neighborhood3r_p"] <- "neighborh_notsafe"

exwas_headache_binary <- exwas(data_train = abcd_gr1, vars = sig_vars_bin, outcome = "medhx_2q_l", data_test = abcd_gr2)
abcd_gr2_weight <- exwas_headache_binary$data_test_exposome
```

# Multivariate models in the main result
```{r}
# Table 3
# set.seed(2023)
mod1 <- glmer(medhx_2q_l ~ (1 | site_id_l_br/rel_family_id/src_subject_id) + 
                 age_years + sex_br + race_black + race_white + ethnicity_hisp,
              nAGQ = 0, family = binomial, data = abcd_gr2_weight) # all population

mod2 <- glmer(medhx_2q_l ~ weighted_exposome + (1 | site_id_l_br/rel_family_id/src_subject_id) + 
                 age_years + sex_br + race_black + race_white + ethnicity_hisp, 
              nAGQ = 0, family = binomial, data = abcd_gr2_weight) # all population

com2 <- tab_model(mod1, mod2)

r2(mod1)[2]
r2(mod2)[2]

anova(mod1, mod2, test="Chisq")

# Cross validation
## Get AUC
AUC <- function(y, yhat) pROC::roc(y~yhat, direction = "<")$auc

clusterVariables <- c("site_id_l_br", "rel_family_id", "src_subject_id")

cv_mod1 <- cv(mod1, k = 10, clusterVariables = clusterVariables, criterion = AUC, seed = 724, ncores = 3)
cv_mod2 <- cv(mod2, k = 10, clusterVariables = clusterVariables, criterion = AUC, seed = 724, ncores = 3)

# Export results
## Number of clusters
cv_mod_main_Table3 <- list(cv_mod1, cv_mod2)
get_n_clusters(cv_mod_main_Table3)

## Coefficients
get_cv_ORs(cv_mod_main_Table3) %>% View()

# Get AUC
get_criteria(cv_mod_main_Table3)$criterion_by_fold %>% View()
get_criteria(cv_mod_main_Table3)$criterion_average %>% View()
```

# Sensitivity analysis # Removed correlated among 21 significant variables at cutoff 0.9
```{r}
# eTable 6
# Remove correlated variables among 21 significant variables at 0.9 cut-off
cor_vars <- abcd_gr1 %>% select(all_of(sig_vars))
corrs = cor_auto(cor_vars)
corr_vars_rm <- findCorrelation(corrs, cutoff = 0.9, exact = T, names = T, verbose = T) #medhx_ss_6i_times_p_l and medhx_6i_l
# Compare row 21  and column  14 with corr  0.983
abcd_gr1_0.9 <- abcd_gr1 %>% select(-all_of(corr_vars_rm)) # remove correlated variables from training dataset abcd_gr1
# Don't need to re-run exwas among new set of variables as all of those were run with the same outcome
# Only medhx_6i_l was removed, thus, we can use sig_vars_bin excluding medhx_6i_l for exposome score (after Dichotomize 2 Likert variables)
sig_vars_bin_0.9 <- sig_vars_bin[!sig_vars_bin %in% corr_vars_rm]

exwas_headache_binary_0.9 <- exwas(data_train = abcd_gr1_0.9, vars = sig_vars_bin_0.9, outcome = "medhx_2q_l", data_test = abcd_gr2)
abcd_gr2_weight_0.9 <- exwas_headache_binary_0.9$data_test_exposome
# Re-run models
mod1_0.9 <- glmer(medhx_2q_l ~ (1 | site_id_l_br/rel_family_id/src_subject_id) + 
                   age_years + sex_br + race_black + race_white + ethnicity_hisp,
              nAGQ = 0, family = binomial, data = abcd_gr2_weight_0.9)

mod2_0.9 <- glmer(medhx_2q_l ~ scale(weighted_exposome) + (1 | site_id_l_br/rel_family_id/src_subject_id) + 
                   age_years + sex_br + race_black + race_white + ethnicity_hisp,
              nAGQ = 0, family = binomial, data = abcd_gr2_weight_0.9)

com1_0.9 <- tab_model(mod1_0.9, mod2_0.9)

# R2
r2(mod1_0.9)[2]
r2(mod2_0.9)[2]

anova(mod1_0.9, mod2_0.9, test="Chisq")

# Cross validation
cv_mod1_0.9 <- cv(mod1_0.9, k = 10, clusterVariables = clusterVariables, criterion = AUC, seed = 724, ncores = 3)
cv_mod2_0.9 <- cv(mod2_0.9, k = 10, clusterVariables = clusterVariables, criterion = AUC, seed = 724, ncores = 3)

# Export results
## Number of clusters
cv_mod_0.9 <- list(cv_mod1_0.9, cv_mod2_0.9)
get_n_clusters(cv_mod_0.9) # May not need # Will remove at the end (remove the function get_n_clusters in utility_fun)

## Coefficients
get_cv_ORs(cv_mod_0.9) %>% View()

# Get AUC
get_criteria(cv_mod_0.9)$criterion_by_fold %>% View()
get_criteria(cv_mod_0.9)$criterion_average %>% View()
```

# Sensitivity analysis # Removed correlated among 21 significant variables at cutoff 0.7
```{r}
# eTable 7
# Remove correlated variables among 21 significant variables at 0.7 cut-off
corr_vars_rm_0.7 <- findCorrelation(corrs, cutoff = 0.7, exact = T, names = T, verbose = T)
# "ple_jail_y"             "medhx_6i_l"             "tbi_ss_worst_overall_l" "ple_separ_y"            "famhx_ss_momdad_dprs_p"

# Compare row 12  and column  5 with corr  0.85 #ple_jail_y & ple_arrest_y
# Compare row 21  and column  13 with corr  0.778 # medhx_6i_l & tbi_ss_worst_overall_l
# Compare row 13  and column  16 with corr  0.73 # tbi_ss_worst_overall_l & tbi_1
# Compare row 6  and column  9 with corr  0.78 # ple_separ_y & ple_step_y
# Compare row 8  and column  11 with corr  0.711 # famhx_ss_momdad_dprs_p & famhx_ss_momdad_alc_p

abcd_gr1_0.7 <- abcd_gr1 %>% select(-all_of(corr_vars_rm_0.7)) # remove correlated variables from training dataset abcd_gr1
sig_vars_bin_0.7 <- sig_vars_bin[!sig_vars_bin %in% corr_vars_rm_0.7]

exwas_headache_binary_0.7 <- exwas(data_train = abcd_gr1_0.7, vars = sig_vars_bin_0.7, outcome = "medhx_2q_l", data_test = abcd_gr2)
abcd_gr2_weight_0.7 <- exwas_headache_binary_0.7$data_test_exposome
# Re-run models
mod1_0.7 <- glmer(medhx_2q_l ~ (1 | site_id_l_br/rel_family_id/src_subject_id) + 
                      age_years + sex_br + race_black + race_white + ethnicity_hisp,
                  nAGQ = 0, family = binomial, data = abcd_gr2_weight_0.7)

mod2_0.7 <- glmer(medhx_2q_l ~ scale(weighted_exposome) + (1 | site_id_l_br/rel_family_id/src_subject_id) + 
                      age_years + sex_br + race_black + race_white + ethnicity_hisp,
                  nAGQ = 0, family = binomial, data = abcd_gr2_weight_0.7)

com1_0.7 <- tab_model(mod1_0.7, mod2_0.7)

# R2
r2(mod1_0.7)[2]
r2(mod2_0.7)[2]

anova(mod1_0.7, mod2_0.7, test="Chisq")

# Cross validation
cv_mod1_0.7 <- cv(mod1_0.7, k = 10, clusterVariables = clusterVariables, criterion = AUC, seed = 724, ncores = 3)
cv_mod2_0.7 <- cv(mod2_0.7, k = 10, clusterVariables = clusterVariables, criterion = AUC, seed = 724, ncores = 3)

# Export results
## Number of clusters
cv_mod_0.7 <- list(cv_mod1_0.7, cv_mod2_0.7)
get_n_clusters(cv_mod_0.7) # May not need # Will remove at the end (remove the function get_n_clusters in utility_fun)

## Coefficients
get_cv_ORs(cv_mod_0.7) %>% View()

# Get AUC
get_criteria(cv_mod_0.7)$criterion_by_fold %>% View()
get_criteria(cv_mod_0.7)$criterion_average %>% View()

save.image("../data/cross_validation_110625.RData")
```





